Data Analysis Methods for the Detection of the Epoch of Reionization

### 2017-10-05 PAPER.tex
corrected some sigloss math

One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out,\alpha} \propto \textbf{e}^{\dagger}\textbf{R}_{e}\textbf{Q}_{\alpha}\textbf{R}_{e}\textbf{e}$. Expanding Equation \ref{eq:sigloss}, we see that $P_{out}$ is comprised of multiple terms:

@@

Taking the case of very large $\textbf{e}$, so that $\textbf{R}_{r} \sim \textbf{R}_{e}$ and any terms involving only $\textbf{x}$ are small, yields:

\begin{eqnarray}
\label{eq:pout_expand}
P_{out, \alpha,\textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{R}_{e}\textbf{Q}_{\alpha}\textbf{R}_{e}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{e}\textbf{Q}_{\alpha}\textbf{R}_{e}\textbf{e} \nonumber \\
&+& \textbf{e}^{\dagger}\textbf{R}_{e}\textbf{Q}_{\alpha}\textbf{R}_{e}\textbf{x}.
\end{eqnarray}

>>>>

One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out,\alpha} \propto \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{e}$. Expanding Equation \ref{eq:sigloss}, we see that $P_{out}$ is comprised of multiple terms:

@@

Taking the case of very large $\textbf{e}$ so that any terms involving only $\textbf{x}$ are small, yields:

\begin{eqnarray}
\label{eq:pout_expand}
P_{out, \alpha,\textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
&+& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{x}.
\end{eqnarray}
